\LARGE \bf Mean Estimation from One-Bit Measurements

### 2021-09-08 abstract.tex
fixed all minor comments from R1

% -*- Mode: latex -*- %
\begin{abstract}
  We consider the problem of estimating the mean of a symmetric log-concave
  distribution under constraint that only a single bit per sample
  from this distribution is available to the estimator. We study the mean
  squared error as a function of the
  sample size (and hence number of bits).
  We consider three settings: first, a centralized setting, where
  an encoder may release $n$ bits given a sample of size $n$, and for
  which there is no asymptotic penalty for quantization; second, an adaptive
  setting  in which each bit is a function of the current
  observation and previously recorded bits, where we show that
  the optimal relative
  efficiency compared to the sample mean is precisely
  the efficiency of the median; lastly, we show that in
  a distributed setting where each bit is only a function
  of a local sample, no estimator can achieve optimal efficiency
  uniformly over the parameter space.
  We additionally complement our results in the adaptive setting
  by showing that \emph{one} round of adaptivity is sufficient
  to achieve optimal mean-square error.
  %% single sample. We show that the optimal efficiency of the adaptive
  %% setting can be attained by splitting the sample into two parts and
  %% allowing only a single adaptation. Otherwise, we show that no one sample
  %% estimation procedure can attain the optimal efficiency uniformly over all
  %% points in the parameter space.  Our results indicate that estimating the
  %% mean from one-bit measurements is equivalent to estimating the sample
  %% median from these measurements. In the adaptive case, this estimate can be
  %% done with vanishing error for any point in the parameter space. In the
  %% distributed case, this estimate can be done with vanishing error only for
  %% a finite number of possible values for the unknown mean.
\end{abstract}

>>>>

% -*- Mode: latex -*- %
\begin{abstract}
  We consider the problem of estimating the mean of a symmetric log-concave
  distribution under the constraint that only a single bit per sample
  from this distribution is available to the estimator. We study the mean
  squared error as a function of the
  sample size (and hence the number of bits).
  We consider three settings: first, a centralized setting, where
  an encoder may release $n$ bits given a sample of size $n$, and for
  which there is no asymptotic penalty for quantization; second, an adaptive
  setting  in which each bit is a function of the current
  observation and previously recorded bits, where we show that
  the optimal relative
  efficiency compared to the sample mean is precisely
  the efficiency of the median; lastly, we show that in
  a distributed setting where each bit is only a function
  of a local sample, no estimator can achieve optimal efficiency
  uniformly over the parameter space.
  We additionally complement our results in the adaptive setting
  by showing that \emph{one} round of adaptivity is sufficient
  to achieve optimal mean-square error.
  %% single sample. We show that the optimal efficiency of the adaptive
  %% setting can be attained by splitting the sample into two parts and
  %% allowing only a single adaptation. Otherwise, we show that no one sample
  %% estimation procedure can attain the optimal efficiency uniformly over all
  %% points in the parameter space.  Our results indicate that estimating the
  %% mean from one-bit measurements is equivalent to estimating the sample
  %% median from these measurements. In the adaptive case, this estimate can be
  %% done with vanishing error for any point in the parameter space. In the
  %% distributed case, this estimate can be done with vanishing error only for
  %% a finite number of possible values for the unknown mean.
\end{abstract}

### 2021-09-08 adaptive-estimation.tex
fixed all minor comments from R1

Then we can adapt the results of Polyak and Juditsky~\cite{PolyakJu92}
on the asymptotic normality of averaged stochastic gradient estimators
to establish the following theorem.
\begin{thm}
  \label{thm:sgd}
  Define the average $\bar{\theta}_n \defeq \frac{1}{n}
  \sum_{i = 1}^n \theta_i$. Assume
  that in a neighborhood
  of $\theta = \mbox{med}(P)$,
  the distribution $P$ has a Lipschitz continuous density $f$.
  Then
  \begin{enumerate}[(i)]
  \item \label{item:normal-sgd}
    Assume that $\left\{ \gamma_n \right\}_{n\in \mathbb N}$ satisfies
    condition~\eqref{eqn:lazy-gamma}.
    Then
    \begin{equation*}
      \sqrt{n}\left( \bar{\theta}_n - \theta\right)
      \cd \normal\left(0,\frac{1}{4 f(0)^2}\right).
    \end{equation*}
    %
    %
  \item \label{item:sgd-regular}
    %(or that $f(x-\theta)$ is differentiable in quadratic mean).  
    Let $\{P_\theta\}_{\theta \in \R}$ be the family of distributions
    with density $f(\cdot - \theta)$, where $f$ has median 0.
    Let $h_n \to h \in \R$, and define the distributions
    $P_n = P_{\theta + h_n/\sqrt{n}}^n$. Then
    \begin{equation*}
      \sqrt{n}\left(\bar{\theta}_n - \theta - h_n / \sqrt{n}\right)
      \mathop{\cd}_{P_n}
      \normal\left(0, \frac{1}{4 f(0)^2}\right),
    \end{equation*}
    and for any bounded, symmetric, and quasi-convex function $L$,
    \begin{align} 
      & \sup_{c < \infty} \limsup_{n \to \infty}
      \sup_{\tau\,:\,|\theta-\tau| \leq \frac{c}{\sqrt{n} }}
      \E_\tau \left[ L\left( \sqrt{n}(\bar{\theta}_{n} - \tau) \right) \right] \nonumber 
      \\
      & \qquad \qquad \qquad \qquad = \mathbb E \left[L(Z/ 2 f(0)) \right],
        \label{eq:attaining_LAM}
    \end{align}
    where $Z \sim \normal(0,1)$. 
    %
    %
  \item \label{item:sgd-ms-convergence} Assume the stepsizes $\gamma_n$
    satisfy both conditions~\eqref{eqn:lazy-gamma}
    and~\eqref{eqn:stringent-gamma}. Let
    $\pi$ be a distribution on $\R$. Then
    \begin{equation*}
      \int \E\Big[( \bar{\theta}_n - \theta )^2\Big] \pi(d\theta)
      = \frac{1}{4 n f(0)^2} + o(n^{-1}). 
    \end{equation*}
  \end{enumerate}
\end{thm}

@@

More formally, we consider the following estimation scheme. Given
$n_1 \in \{1, \ldots, n\}$,
set the individual bits
\begin{equation*}
  B_i =
  \begin{cases}
    \indic{X_i \le \theta_0} & i = 1,\ldots,n_1, \\
    \indic{X_i \le T_n}& i={n_1+1,\ldots,n},
  \end{cases}
\end{equation*}
where
\begin{equation*}
  T_n \defeq \theta_0 - F^{-1}\left(
  \frac{1}{n_1} \sum_{i=1}^{n_1} B_i 
  \right)
  ~~ \mbox{and} ~~
  \theta_n \defeq
  T_n - F^{-1} \left(\frac{1}{n - n_1}
  \sum_{i = n_1}^n B_i \right).
\end{equation*} 
The intuition here is that the estimator $\theta_n$ is a one-step
correction (cf.~\cite[Thm.~6.4.3]{LehmannCa98}) of the initial estimator
$T_n$, which approximately estimates
$\theta_0 - F^{-1}(\theta_0 - \theta) = \theta$. We then have the
following convergence result.
\begin{thm}
  Assume that $X_i = Z_i + \theta$, where $Z_i$ are i.i.d.\
  with density $f$ and CDF $F$ and $\mbox{med}(Z_i) = 0$. Assume that
  $f$ is continuous at 0, and that as $n \to \infty$,
  $n_1(n) \rightarrow \infty$ and $n_1 / n \to
  0$. Then
  \begin{align*}
    \sqrt{n} \left( {\theta}_n - \theta  \right)
    \cd  \normal\left( 0, \frac{1}{4 f(0)^2}\right).
  \end{align*}
\end{thm}
\noindent
That is, under Assumption~\ref{assump:failure_rate}, the method is
asymptotically optimal.
%
\begin{proof}
  We abuse notation and instead of assuming we receive $n$ observations, assume
  we receive the $n + n_1$ observations $X_{-n_1}, \ldots, X_{-1}$ and
  $X_1, \ldots, X_n$, defining $T_n = \theta_0 - F^{-1}(\frac{1}{n_1}
  \sum_{i = -n_1}^{-1} B_i)$ and
  $B_i = \indic{X_i \le T_n}$ for $i \ge 1$.
  Letting $X_i = Z_i + \theta$ for $Z_i$ i.i.d.\ with fixed density
  $f = F'$, we have
  $B_i \cas F(\theta_0 - \theta)$, so that
  $\frac{1}{n_1} \sum_{i = -n_1}^{-1} B_i \cas F(\theta - \theta_0)$ and
  by the continuous
  mapping theorem we have $T_n \cas \theta$ as $n_1 \to \infty$.

>>>>

Then we can adapt the results of Polyak and Juditsky~\cite{PolyakJu92}
on the asymptotic normality of averaged stochastic gradient estimators
to establish the following theorem.
\begin{thm}
  \label{thm:sgd}
  Define the average $\bar{\theta}_n \defeq \frac{1}{n}
  \sum_{i = 1}^n \theta_i$. Assume
  that in a neighborhood
  of $\theta = \mbox{med}(P)$,
  the distribution $P$ has a Lipschitz continuous density $f$.
  Then
  \begin{enumerate}[(i)]
  \item \label{item:normal-sgd}
    Assume that $\left\{ \gamma_n \right\}_{n\in \mathbb N}$ satisfies
    condition~\eqref{eqn:lazy-gamma}.
    Then
    \begin{equation*}
      \sqrt{n}\left( \bar{\theta}_n - \theta\right)
      \cd \normal\left(0,\frac{1}{4 f(0)^2}\right).
    \end{equation*}
    %
    %
  \item \label{item:sgd-regular}
    %(or that $f(x-\theta)$ is differentiable in quadratic mean).  
    Let $\{P_\theta\}_{\theta \in \R}$ be the family of distributions
    with density $f(\cdot - \theta)$, where $f$ has median 0.
    Let $h_n \to h \in \R$, and define the distributions
    $P_n = P_{\theta + h_n/\sqrt{n}}^n$. Then
    \begin{equation*}
      \sqrt{n}\left(\bar{\theta}_n - \theta - h_n / \sqrt{n}\right)
      \mathop{\cd}_{P_n}
      \normal\left(0, \frac{1}{4 f(0)^2}\right),
    \end{equation*}
    and for any bounded, symmetric, and quasi-convex function $L$,
    \begin{align} 
      & \sup_{c < \infty} \limsup_{n \to \infty}
      \sup_{\tau\,:\,|\theta-\tau| \leq \frac{c}{\sqrt{n} }}
      \E_\tau \left[ L\left( \sqrt{n}(\bar{\theta}_{n} - \tau) \right) \right] \nonumber 
      \\
      & \qquad \qquad \qquad \qquad = \mathbb E \left[L(Z/ 2 f(0)) \right],
        \label{eq:attaining_LAM}
    \end{align}
    where $Z \sim \normal(0,1)$. 
    %
    %
  \item \label{item:sgd-ms-convergence} Assume the stepsizes $\gamma_n$
    satisfy both conditions~\eqref{eqn:lazy-gamma}
    and~\eqref{eqn:stringent-gamma}. Let
    $\pi$ be a distribution on $\R$ \newtext{with a finite second moment}. Then
    \begin{align}
      \int \E\Big[( \bar{\theta}_n - \theta )^2\Big] \pi(d\theta)
      = \frac{1}{4 n f(0)^2} + o(n^{-1}). 
      \label{eq:adaptive_3}
    \end{align}
  \end{enumerate}
\end{thm}

@@

More formally, we consider the following estimation scheme. Given
$n_1 \in \{1, \ldots, n\}$,
set the individual bits
\begin{equation*}
  B_i =
  \begin{cases}
    \indic{X_i \le \theta_0} & i = 1,\ldots,n_1, \\
    \indic{X_i \le T_n}& i={n_1+1,\ldots,n},
  \end{cases}
\end{equation*}
where
\begin{equation*}
  T_n \defeq \theta_0 - F^{-1}\left(
  \frac{1}{n_1} \sum_{i=1}^{n_1} B_i 
  \right)
  ~~ \mbox{and} ~~
  \theta_n \defeq
  T_n - F^{-1} \left(\frac{1}{n - n_1}
  \sum_{i = n_1}^n B_i \right).
\end{equation*} 
The intuition here is that the estimator $\theta_n$ is a one-step
correction (cf.~\cite[Thm.~6.4.3]{LehmannCa98}) of the initial estimator
$T_n$, which approximately estimates
$\theta_0 - F^{-1}(\theta_0 - \theta) = \theta$. We then have the
following convergence result.
\begin{thm}
  Assume that $X_i = Z_i + \theta$, where $Z_i$ are i.i.d.\
  with density $f$ and CDF $F$ and $\mbox{med}(Z_i) = 0$. Assume that
  $f$ is continuous at 0, and that as $n \to \infty$,
  $n_1(n) \rightarrow \infty$ and $n_1 / n \to
  0$. Then
  \begin{align*}
    \sqrt{n} \left( {\theta}_n - \theta  \right)
    \cd  \normal\left( 0, \frac{1}{4 f(0)^2}\right).
  \end{align*}
\end{thm}
\noindent
That is, under Assumption~\ref{assump:failure_rate}, the method is
asymptotically optimal.
%
\begin{proof}
  We abuse notation and instead of assuming we receive $n$ observations, assume
  we receive the $n + n_1$ observations $X_{-n_1}, \ldots, X_{-1}$ and
  $X_1, \ldots, X_n$, defining $T_n = \theta_0 - F^{-1}(\frac{1}{n_1}
  \sum_{i = -n_1}^{-1} B_i)$ and
  $B_i = \indic{X_i \le T_n}$ for $i \ge 1$.
  Letting $X_i = Z_i + \theta$ for $Z_i$ i.i.d.\ with fixed density
  $f = F'$, we have
  $\ex{B_i} \cas F(\theta_0 - \theta)$, so that
  $\frac{1}{n_1} \sum_{i = -n_1}^{-1} B_i \cas F(\theta - \theta_0)$ and
  by the continuous
  mapping theorem we have $T_n \cas \theta$ as $n_1 \to \infty$.

### 2021-09-08 distributed-estimation.tex
fixed all minor comments from R1

We begin by making a few restrictions on the collections of the sets $A_i$,
which we believe not unreasonable, but which allow us to develop fundamental
limits for estimation.  We require a bit of notation to define the
assumptions. As we work with a location family based on a density $f$
with associated probability distribution $P$ on variables $Z$,
we define
\begin{equation*}
  P_\theta(A) \defeq P(Z - \theta \in A)
\end{equation*}
for $Z$ with density $f$. Whenever $A$ is a collection
of disjoint intervals $A = \cup_i \{[t_i^-, t_i^+]\}$, we may define
\begin{equation*}
  \dPtheta(A) \defeq \frac{\partial}{\partial \theta} P_\theta(A)
  = \sum_i \left(f(t_i^- - \theta) - f(t_i^+ - \theta)\right),
\end{equation*}
and similarly we define the score
function $\score_\theta(A) \defeq \dPtheta(A) / P_\theta(A)$.
For $B = \indic{X \in A}$, we abuse notation and also write
$\score_\theta(B) = \score_\theta(A)$ and similarly for $\dPtheta$.
With this, we may define the variance of the
scores $\score_\theta(B_i)$ under $P_\theta$ via
\begin{equation}
  \label{eq:precision_general}
  L_n(A_1,\ldots,A_n;\theta) \defeq
  \frac{1}{n} \sum_{i=1}^n \frac{ \dPtheta(A_i)^2}{
    P_\theta(A_i) (1 - P_\theta(A_i))}.
\end{equation}
We then make the following assumption.
\begin{assumption}
  \label{assumption:detection-regions}
  The density and detection regions satisfy
  \begin{enumerate}[(i)]
  \item \label{item:lipschitz-density}
    The density function $f$ of $X_n - \theta$ is Lipschitz continuous.
  \item \label{item:finite-intervals}
    Each set $A_n$ is the finite union of $k_n$ disjoint intervals
    (which may include $\pm \infty$), where
    \begin{equation*}
      \frac{1}{n} \cdot \max_{i \le n} \frac{k_i^3}{P_\theta(A_i)^4
        (1 - P_\theta(A_i))^4} \to 0.
    \end{equation*}
    %% Each set $A_n$ is a finite union of at most $K < \infty$ intervals
    %% (which may include $\pm \infty$), and
    %% $0 < \inf_n P_\theta(A_n) \le \sup_n P_\theta(A_n) < 1$.
  \item \label{item:limit-variance}
    The limit
    \begin{equation}
      \label{eqn:LAN-limit}
      \kappa(\theta) \defeq \lim_{n\to \infty} L_n(A_1,\ldots,A_n; \theta)
    \end{equation}
    exists and is finite.
  \end{enumerate}
\end{assumption}

@@

When the conclusions of Corollary~\ref{cor:LAN_thresh} hold, local asymptotic normality of $\{B_n\}_{n=1}^\infty$ implies that the maximum
likelihood estimator (ML) of $\theta$ from $B_1,\ldots,B_n$, denoted here by
${\theta}^{ML}_n$, is local asymptotic minimax in the sense that
\begin{equation*}
  \sqrt{n} \left( {\theta}^{ML}_n - \theta \right)
  \cd \normal\left(0, 1/\kappa(\theta) \right). 
\end{equation*}
We note that ${\theta}^{ML}_n$ solves
\begin{equation}
  \label{eq:ML}
  0 = \sum_{i=1}^n B_i \frac{f \left( t_i-\theta\right) }{F \left(B_i  (t_i-\theta)\right) }.
\end{equation}
If the collection $\{t_1,t_2\ldots\}$ is bounded
(for example $\{t_1,t_2\ldots\} \subset \Theta$), then
\begin{equation*}
\lim_{n\to \infty} n \cdot \ex{\left({\theta}^{ML}_n - \theta \right)^2}  = 1/\kappa(\theta), 
\end{equation*} 
so that the ML estimator attains the local asymptotic MSE of Theorem~\ref{thm:adpative_lower_bound}.

@@

We conclude this section by considering the density of the threshold values
that maximizes the worst-case information $\inf_\theta \kappa(\theta)
= \kappa_\lambda(\theta)$ where $\kappa_\lambda(\theta)
= \int \eta(t - \theta) d\lambda(t)$.
This distribution $\lambda$ solves the
optimization problem
\begin{align}
  \label{eq:var_cvx_minimax}
  \begin{split}
    \mathrm{maximize} \quad &  \inf_{\theta \in \Theta} \int \eta(t-\theta) \lambda(dt)
    \\ 
    \mathrm{subject~to} 
    \quad & \lambda(dt)\geq 0,\quad \int \lambda(dt) \leq 1. 
  \end{split}
\end{align}
The objective function~\eqref{eq:var_cvx_minimax} is concave in
$\lambda(dt)$ and continuous in the weak topology over measures on $\Theta$,
so that by discretizing, we can approximately solve this problem using
convex optimization. We let $\kappa^\star$ denote the maximal value of
problem~\eqref{eq:var_cvx_minimax} and $\lambda^\star(dt)$ be the density
achieving the maximum. By drawing thresholds
$t_i \simiid \lambda^\star$,
Corollary~\ref{cor:LAN_thresh} guarantees that for any $\theta \in \Theta$, the
maximum likelihood estimator
using $\{B_i = \sgn(X_i - t_i)\}_{i \in \N}$ is at least $\kappa^\star$. \par
%
Figure~\ref{fig:minimax_support} illustrates an approximation to
$\lambda^\star(dt)$ obtained by solving a discretized version of
\eqref{eq:var_cvx_minimax} for the case when $f(x)$ is the normal density
with variance $\sigma^2$ and $\Theta = [-1/2,1/2]$. The minimax asymptotic
precision parameter $\kappa^\star$ obtained this way is illustrated in
Fig.~\ref{fig:minimax_ARE} as a function of $\sigma$. Also
illustrated in these figures is $\kappa_{\unif}$, the precision
parameter corresponding to threshold values uniformly distribution over
$\Theta$,
\begin{align}
& \kappa_{\unif} \triangleq \min_{\theta \in [-T,T]} \frac{1}{2T}\int_{-T}^T \eta\left(t-\theta\right) dt \nonumber
 \\
& = 
\frac{1}{2T}\int_{-T}^{T} \eta\left(t\pm T\right) dt
= \frac{1}{2T}\int_{0}^{2T} \eta(t) dt  \label{eq:uniform_risk}. 
\end{align}

>>>>

We begin by making a few restrictions on the collections of the sets $A_i$,
which we believe not unreasonable, but which allow us to develop fundamental
limits for estimation.  We require a bit of notation to define the
assumptions. As we work with a location family based on a density $f$
with associated probability distribution $P$ on variables $Z$,
we define
\begin{equation*}
  P_\theta(A) \defeq P(Z - \theta \in A)
\end{equation*}
for $Z$ with density $f$. Whenever $A$ is a collection of disjoint intervals $A = \cup_i [t_i^-, t_i^+]$, we may define
\begin{equation*}
  \dPtheta(A) \defeq \frac{\partial}{\partial \theta} P_\theta(A)
  = \sum_i \left(f(t_i^- - \theta) - f(t_i^+ - \theta)\right),
\end{equation*}
and similarly we define the score
function $\score_\theta(A) \defeq \dPtheta(A) / P_\theta(A)$.
For $B = \indic{X \in A}$, we abuse notation and also write
$\score_\theta(B) = \score_\theta(A)$ and similarly for $\dPtheta$.
With this, we may define the variance of the
scores $\score_\theta(B_i)$ under $P_\theta$ via
\begin{equation}
  \label{eq:precision_general}
  L_n(A_1,\ldots,A_n;\theta) \defeq
  \frac{1}{n} \sum_{i=1}^n \frac{ \dPtheta(A_i)^2}{
    P_\theta(A_i) (1 - P_\theta(A_i))}.
\end{equation}
We then make the following assumption.
\begin{assumption}
  \label{assumption:detection-regions}
  The density and detection regions satisfy
  \begin{enumerate}[(i)]
  \item \label{item:lipschitz-density}
    The density function $f$ of $X_n - \theta$ is Lipschitz continuous.
  \item \label{item:finite-intervals}
    Each set $A_i$ is the finite union of $k_i$ disjoint intervals
    (which may include $\pm \infty$), where
    \begin{equation*}
      \frac{1}{n} \cdot \max_{i \le n} \frac{k_i^3}{P_\theta(A_i)^4
        (1 - P_\theta(A_i))^4} \to 0.
    \end{equation*}
    %% Each set $A_n$ is a finite union of at most $K < \infty$ intervals
    %% (which may include $\pm \infty$), and
    %% $0 < \inf_n P_\theta(A_n) \le \sup_n P_\theta(A_n) < 1$.
  \item \label{item:limit-variance}
    The limit
    \begin{equation}
      \label{eqn:LAN-limit}
      \kappa(\theta) \defeq \lim_{n\to \infty} L_n(A_1,\ldots,A_n; \theta)
    \end{equation}
    exists and is finite.
  \end{enumerate}
\end{assumption}

@@

When the conclusions of Corollary~\ref{cor:LAN_thresh} hold, local asymptotic normality of $\{B_n\}_{n=1}^\infty$ implies that the maximum
likelihood estimator (ML) of $\theta$ from $B_1,\ldots,B_n$, denoted here by
${\theta}^{ML}_n$, is local asymptotic minimax in the sense that
\begin{equation*}
  \sqrt{n} \left( {\theta}^{ML}_n - \theta \right)
  \cd \normal\left(0, 1/\kappa(\theta) \right). 
\end{equation*}
We note that ${\theta}^{ML}_n$ solves
\begin{equation}
  \label{eq:ML}
  0 = \sum_{i=1}^n B_i \frac{f \left( t_i-\theta\right) }{F \left(B_i  (t_i-\theta)\right) }.
\end{equation}
If the collection $\{t_1,t_2\ldots\}$ is bounded
(for example $\{t_1,t_2\ldots\} \subset \Theta$), then
\begin{equation*}
\lim_{n\to \infty} n \cdot \ex{\left({\theta}^{ML}_n - \theta \right)^2}  = 1/\kappa(\theta), 
\end{equation*} 
so that the ML estimator attains the local asymptotic MSE of Theorem~\ref{theorem:non-adaptive-minimax}.

@@

We conclude this section by considering the \newtext{distribution} of the threshold values
that maximizes the worst-case information $\inf_\theta \kappa(\theta)
= \kappa_\lambda(\theta)$ where $\kappa_\lambda(\theta)
= \int \eta(t - \theta) d\lambda(t)$.
The \newtext{optimal distribution $\lambda^\star$} solves the
optimization problem
\begin{align}
  \label{eq:var_cvx_minimax}
  \begin{split}
    \mathrm{maximize} \quad &  \inf_{\theta \in \Theta} \int \eta(t-\theta) \lambda(dt)
    \\ 
    \mathrm{subject~to} 
    \quad & \lambda(dt)\geq 0,\quad \int \lambda(dt) \leq 1. 
  \end{split}
\end{align}
The objective function~\eqref{eq:var_cvx_minimax} is concave in
$\lambda(dt)$ and continuous in the weak topology over measures on $\Theta$,
so that by discretizing, we can approximately solve this problem using
convex optimization. We let $\kappa^\star$ denote the maximal value of
problem~\eqref{eq:var_cvx_minimax} and $\lambda^\star(dt)$ be the density
achieving the maximum. By drawing thresholds
$t_i \simiid \lambda^\star$,
Corollary~\ref{cor:LAN_thresh} guarantees that for any $\theta \in \Theta$, the
maximum likelihood estimator
using $\{B_i = \sgn(X_i - t_i)\}_{i \in \N}$ is at least $\kappa^\star$. \par
%
Figure~\ref{fig:minimax_support} illustrates an approximation to
$\lambda^\star(dt)$ obtained by solving a discretized version of
\eqref{eq:var_cvx_minimax} for the case when $f(x)$ is the normal density
with variance $\sigma^2$ and $\Theta = [-1/2,1/2]$. The minimax asymptotic
precision parameter $\kappa^\star$ obtained this way is illustrated in
Fig.~\ref{fig:minimax_ARE} as a function of $\sigma$. Also
illustrated in these figures is $\kappa_{\unif}$, the precision
parameter corresponding to threshold values uniformly distribution over
$\Theta$,
\begin{align}
& \kappa_{\unif} \triangleq \min_{\theta \in [-T,T]} \frac{1}{2T}\int_{-T}^T \eta\left(t-\theta\right) dt \nonumber
 \\
& = 
\frac{1}{2T}\int_{-T}^{T} \eta\left(t\pm T\right) dt
= \frac{1}{2T}\int_{0}^{2T} \eta(t) dt  \label{eq:uniform_risk}. 
\end{align}
